Title

### 2014-11-14 manuscript.tex
Fixed some typos

Notice that the computed effect is concentrated around each point mass (black
dots) and does not resemble the effect of a tesseroid.

@@

@@

The size of the tesseroid is used as proxy for the distance between point
masses.

>>>>

Notice that the computed effect is concentrated around each point mass
of the GLQ (black dots) and does not resemble the effect of a tesseroid.

@@

The computed $g_{xy}$ component more closely resembles the results from
\citet{Asgharzadeh2007}.

@@

The size of the tesseroid is used as a proxy for the distance between point
masses.
